Topic Scores

### 2019-02-20 test_delete_later_sofia.Rmd
test key word selection

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
library(tidyverse)
```
##Raw Data
```{r setup, include=FALSE}
#
##d_course and d_transcript
load("Output/data_pillar_1.RDATA")

@@

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

@@

#
##key word Contributions to Topic
 contribution_to_topics <- beta_description$k35                       %>%
  filter(term %in% student$kw_policy)                                 %>%
  arrange(topic, desc(beta))                                          %>%
  spread(key=topic, value=beta)                                       %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)                                      %>%
   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))

@@

>>>>

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
library(tidyverse)
```

##Raw Data
```{r setup, include=FALSE}
#
##d_course and d_transcript
load("Output/data_pillar_1.RDATA")

@@

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)

@@

#
##key word Contributions to Topic
 contribution_to_topics #<- 
beta_description$k35                       %>%
  filter(term %in% student$kw_policy)                                 %>%
  arrange(topic, desc(beta))                                          %>%
  group_by(topic) %>%
  #this is new
  mutate(beta_sum=sum(beta),
         beta_rank=beta/beta_sum) %>%
  select(-beta_sum, -beta)
  #
  spread(key=topic, value=beta)                                       %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)                                      %>%
   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))

  beta_description$k35                       %>%
  filter(term %in% student$kw_policy)                                 %>%
  arrange(topic, desc(beta))                                          %>%
  spread(key=topic, value=beta)                                       %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)                                      %>%
   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))

@@

###Selecting key words
```{r}
test <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(3, beta) %>%
  group_by(topic) %>%
  summarise(key_words= list(Reduce(f= c, x = term)))

kw <- unique(Reduce(x = test$key_words, f= c))

kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl")

setdiff(kw, kw_stopwords)
